{\fontfamily{ptm}\selectfont Reading Notes}

### 2025-05-09 Notebook LaTEX/Formalized Notes/Notes 2025 03/main.tex
>w<, changes

                We define $F$ to be $q$ weakly convex if there exists $q \in \ge 0$ such that the function $F + q/2\Vert \cdot\Vert^2$ is a convex function and $q$ is the infimum of all such possible parameters. 

@@

                            $f: \RR^n \rightarrow \RR$ & \\
                            $g: \RR^n \rightarrow \overline \RR$ & \\
                            $\tilde x \in \RR^n$ & \\
                            $x \in \RR^n$ & \\
                            $\rho$ & Number $\rho \in (0, 1)$ \\

@@

    \section{Practical enhancement from the Nesterov's Monotone Variant}
        Firstly, we will introduce some theories in for nonconvex functions. 
        This is necessary because Nesterov's monotone variants can adapt to weakly convex objective functions. 
        The following assumption will characterize the full scope of discussion in nonconvexity objective function. 
        \begin{definition}[nonconvex Nesterov's monotone scheme]\;\label{def:nes-monotone-scheme}\\

        \end{definition}
    \section{Restarting with function values}
    \section{Applying them to large scale LP}

>>>>

                We define $F$ to be $q$ weakly convex if there exists $q \ge 0$ such that the function $F + q/2\Vert \cdot\Vert^2$ is a convex function and $q$ is the infimum of all such possible parameters. 

@@

                            $f: \RR^n \rightarrow \RR$ & Convex Smooth\\
                            $\tilde x \in \RR^n$ & Vector\\
                            $\rho$ & Number $\rho \in (0, 1)$ Number\\

@@

    \section{Practical enhancement from the Nesterov's Monotone Variant}
        Firstly, we will introduce some theories in for nonconvex functions. 
        This is necessary because Nesterov's monotone variants can adapt to weakly convex objective functions. 
        The following assumption will characterize the full scope of discussion in nonconvexity objective function. 
        \begin{definition}[nonconvex Nesterov's monotone scheme]\;\label{def:nes-monotone-scheme}\\
            ...
        \end{definition}
    \section{Restarting with function values}
    \section{Applying them to large scale LP}
